\section{Introduction}
\label{sec:intro}

Much of the effort involved in using an HPC system happens around the batch job itself. Users inspect logs, repair scripts, install dependencies, sort through output, and decide what to run next. These are natural tasks for an LLM agent with access to files, command-line tools, and scheduler commands. Several recent systems connect agents to HPC resources and scientific workflows \cite{Ma2025HPCAgent,Rosendo2025ORNL,Dawson2026LARA}; another uses multiple agents to build and repair HPC software \cite{Mondesire2025PEARC}. Adoption is also occurring outside research prototypes. Aalto Scientific Computing, for example, has published guidance for users running agentic coding tools on its Triton cluster \cite{AaltoSciComp2026}.

Giving an agent enough access to be useful also gives untrusted material a new route to that access. A debugging agent must read the output of a failed job. A build agent must interpret compiler messages and package metadata. A workflow agent may exchange files or messages with other agents. If any of this material contains adversarial instructions, the agent may act on them using the authority it received from the user. The resulting commands can be valid from the operating system's point of view and still be outside the user's intended task.

Agent-security research provides a good account of the underlying mechanisms. Indirect prompt injection can manipulate applications that consume untrusted content \cite{Greshake2023PromptInjection}; tool-using agents can take harmful actions \cite{Ruan2024ToolEmu}; and benchmarks can measure both task completion and resistance to attack \cite{Debenedetti2024AgentDojo}. Tool descriptions and inter-agent protocols add further avenues for manipulation \cite{Shi2025ToolHijacker,Ferrag2025ProtocolExploits,Wang2026PILandscape}. Most evaluations, however, use settings such as email, banking, travel, or generic tool sandboxes. They do not model scheduler allocations, parallel filesystems, or accounts that legitimately span several scientific projects.

HPC security starts from a different concern: deciding which principals may use which resources. Zone-based architectures separate access, management, compute, and storage functions \cite{NIST2024SP800223}. Deployed systems isolate users' processes, files, network traffic, and accelerators \cite{Prout2024UserSeparation}, while federated identity and zero-trust designs strengthen authentication and access control across facilities \cite{Alam2024ZeroTrust}. These controls remain necessary. Yet an access check cannot determine whether a permitted command reflects the user's request or an instruction copied from a poisoned log into the agent's context.

Our concern lies between these two lines of work. The identity and credentials may be valid, and each action may pass the site's authorization checks, while the sequence of actions no longer serves the task the user assigned. We call an agent in this state a \emph{hijacked authorized agent}.

\subsection{Position}
\label{sec:thesis}

Our position rests on three observations:

\begin{enumerate}[leftmargin=*]
  \item HPC changes the practical meaning of a successful prompt-injection attack. Scheduler authority, durable shared storage, multi-project access, and scientific provenance introduce consequences that are absent from many current agent benchmarks.
  \item Neither neighboring literature measures the complete problem. Agent-security benchmarks omit important HPC resources and policies, while HPC controls do not test whether adversarial content can redirect an authenticated agent.
  \item The question is already relevant to deployed systems. Agents are being used in HPC workflows \cite{Ma2025HPCAgent,Rosendo2025ORNL,Mondesire2025PEARC}, and at least one computing center has begun documenting the associated risks \cite{AaltoSciComp2026}. Evaluation should develop alongside adoption rather than after local practices have hardened.
\end{enumerate}

\subsection{Contributions}
\label{sec:contributions}

\begin{enumerate}[leftmargin=*]
  \item We define the \textbf{hijacked authorized agent} threat model and distinguish it from privilege escalation and generic indirect prompt injection (Section~\ref{sec:threat-model}).
  \item We organize the relevant HPC attack surfaces into five groups: shared-filesystem poisoning, scheduler and log channels, tool/module/MCP poisoning, cross-project leakage, and multi-agent exfiltration (Section~\ref{sec:taxonomy}).
  \item We compare these surfaces with existing HPC and agent-monitoring controls (Section~\ref{sec:defense-gap}).
  \item We identify open research problems and describe TaskBound, a companion benchmark now under development (Section~\ref{sec:research-agenda}).
\end{enumerate}

\subsection{Scope}
\label{sec:scope}

This is a threat characterization and research agenda, not an empirical evaluation. We do not report attack success rates, assess a particular model or framework, or present a complete defense. Training-time poisoning, weight extraction, GPU side channels, kernel or hypervisor compromise, and general content-safety jailbreaks are also outside our scope. The narrower question here is how content from the HPC environment can redirect an agent that already holds valid credentials.
