\section{Background}
\label{sec:background}

\subsection{LLM agents are entering HPC}
\label{sec:background-hpc}

Several projects now place LLM agents in direct contact with HPC infrastructure. Ma et al.\ connect LangChain and LangGraph agents to HPC resources through Parsl and demonstrate molecular-dynamics workflows on ALCF's Polaris system \cite{Ma2025HPCAgent}. Rosendo et al.\ combine an LLM interface, multi-agent decision making, facility APIs, and provenance services for experiments spanning two ORNL user facilities \cite{Rosendo2025ORNL}. Mondesire et al.\ use a multi-agent system to build and repair more than 200 HPC software packages \cite{Mondesire2025PEARC}. In the last example, compiler errors and build logs are not incidental output; they are inputs to the next decision made by the agent.

Dawson et al.\ identify correctness, reproducibility, and safe resource use as open problems for agentic supercomputing workflows \cite{Dawson2026LARA}. Similar concerns have reached site documentation. Aalto Scientific Computing notes the use of Claude Code and OpenAI Codex for coding and Slurm job management on Triton, and warns users about prompt injection, malicious skills, external code, and confidentiality \cite{AaltoSciComp2026}. The systems literature nevertheless remains focused mainly on capability, orchestration, and provenance. It offers little evidence about behavior when routine inputs such as logs or tool output are malicious.

\subsection{LLM-agent security: known attack mechanisms}
\label{sec:background-agent-security}

The underlying attack mechanisms have been studied mostly outside HPC. Greshake et al.\ showed that instructions embedded in retrieved content, rather than supplied by the user, can change an LLM-integrated application's behavior and lead to data disclosure or persistent compromise \cite{Greshake2023PromptInjection}. ToolEmu evaluates harmful actions by tool-using agents in an LM-emulated sandbox \cite{Ruan2024ToolEmu}. AgentDojo provides a reproducible benchmark with 97 tasks and 629 security test cases across email, banking, travel, and workspace applications \cite{Debenedetti2024AgentDojo}. Its joint measurement of task utility and attack success is particularly useful for our proposed benchmark (Section~\ref{sec:benchmark}).

Recent work broadens the picture. Ferrag et al.\ survey attacks that include inter-agent protocol exploits \cite{Ferrag2025ProtocolExploits}, and Wang et al.\ systematize prompt-injection threats and their defenses \cite{Wang2026PILandscape}. Shi et al.\ show that a malicious tool description can steer an agent toward an attacker-controlled tool without requiring white-box access to the model \cite{Shi2025ToolHijacker}. This result is relevant to environment modules, shared utilities, and MCP tool servers (Section~\ref{sec:tool-poisoning}). Still, an email inbox or travel itinerary does not exercise scheduler authority, project allocations, or filesystem state shared across jobs and users. Those differences affect both the available attacks and the definition of a policy violation.

\subsection{HPC security: established controls and their assumptions}
\label{sec:background-hpcsec}

HPC security has developed strong controls around identities and resources. NIST SP 800-223 organizes HPC infrastructure into access, management, compute, and storage zones and analyzes threats to each \cite{NIST2024SP800223}. Prout et al.\ describe user separation at the MIT Lincoln Laboratory Supercomputing Center across processes, files, network traffic, and accelerators \cite{Prout2024UserSeparation}. Alam et al.\ present a federated single-sign-on and zero-trust design for AI and HPC research infrastructure, including multi-factor authentication and time-limited role-based access \cite{Alam2024ZeroTrust}.

These mechanisms determine who may access a resource and under what conditions. They generally treat a successful authorization decision as sufficient evidence that the action is allowed. For an LLM agent, that inference is incomplete. A POSIX check or scheduler record cannot tell whether the user requested an action or whether the agent derived it from adversarial text in a log. The site sees the same account in either case. The missing information is the scope and origin of the task that led to the action.
