\section{Threat Model: The Hijacked Authorized Agent}
\label{sec:threat-model}

\subsection{Definition}
\label{sec:threat-def}

We call an agent \textbf{hijacked} when content encountered during ordinary operation causes it to act outside its assigned task, even though the user's account and the agent's tool configuration permit each individual action. The content might appear in a file, a job log, tool output, or a message from another agent. No conventional privilege escalation is required: the attacker need not obtain root access, bypass POSIX permissions, or steal credentials.

Consider an agent asked to diagnose a failed job in project A. The user may also belong to project B and may be allowed to submit jobs to several partitions. If a poisoned log leads the agent to read project B or launch an unrelated job, the operating system and scheduler may record nothing more than permitted activity by that user. The violated boundary is the authority implied by the debugging task, not the standing authority of the account. Conventional HPC controls do not usually encode that task boundary in a form they can enforce or audit.

\subsection{Assumptions}
\label{sec:threat-assumptions}

\begin{itemize}[leftmargin=*]
  \item the user intentionally and legitimately launches the agent for a specific task;
  \item the agent has valid, correctly provisioned access to its assigned workspace and tools;
  \item the cluster control plane, scheduler, and any benchmark or monitoring harness are trusted;
  \item the attacker does not have root access and does not modify model weights;
  \item the attacker's only foothold is the ability to influence content the agent will read, execute, or receive during normal operation, such as a file, a log, a tool's output, shared state, or a message from another agent.
\end{itemize}

\subsection{Attacker capability classes}
\label{sec:threat-capabilities}

Table~\ref{tab:capabilities} lists the attacker footholds considered here. Stating the foothold matters because an attack that already assumes unauthorized filesystem or administrator access demonstrates a conventional access-control failure, not the failure mode defined above.

\begin{table}[H]
\centering
\caption{Attacker capability classes considered by the hijacked authorized agent threat model.}
\label{tab:capabilities}
\begin{tabularx}{\linewidth}{@{} l X X @{}}
\toprule
\textbf{Class} & \textbf{Capability} & \textbf{Representative HPC source} \\
\midrule
C1 & Write or influence a scientific artifact the agent will read & simulation log, metadata field, README, result file \\
C2 & Influence scheduler-adjacent output & job stdout/stderr, wrapper diagnostics, accounting note \\
C3 & Control a tool's description or output & build helper, converter, module description, MCP tool server \\
C4 & Write to shared node or filesystem state & scratch space, cache, shared collaboration path \\
C5 & Control or hijack a peer agent & inter-agent message, staged intermediate artifact \\
\bottomrule
\end{tabularx}
\end{table}
